|

### 2021-12-01 paper/dcpo_demsupport.Rmd
Modify the part about SEM and adverse effect of measurement errors on coef

We proceed in three steps.
First, we reproduce the original analyses of Claassen [-@Claassen2020a; -@Claassen2020b], which included only the point estimates of the latent variable of democratic support and so exclude its measurement uncertainty.
Second, we collect the original cross-national survey data, replicate the latent variable measure of democratic support used in the two articles, and conduct the articles' analyses again, this time maintaining the entire distribution of estimates of democratic support in each country-year.^[Additional details on this data replication process are found in Supplementary Information Appendix \@ref(dgp).]
As democracy is also a latent variable in these analyses, we include the uncertainty in its estimates as well, along with that for corruption in the models of @Claassen2020b.
In the third step, we collect even more survey data---increasing these source data by one-third---and re-estimate the two articles' analyses once more, again maintaining the full distribution of estimates to preserve measurement uncertainty.^[We also attempted to make fuller use of the available survey data by employing the DCPO model [@Solt2020a], which unlike the [@Claassen2019] model does not dichotomize ordinal responses.  The better fit of the DCPO model to the data on democratic support [see @Solt2020a, 10-12] and the additional information it incorporates, however, did not yield substantively different results; see Supplementary Information Appendix \@ref(dcpo).]

@@

Although measurement uncertainty has not yet attracted attention in the field of comparative public opinion [see, in addition to the works examined here, @OGrady2019], latent variables are estimated with a quantifiable amount of measurement uncertainty, and ignoring that uncertainty in analyses can both attenuate or exaggerate coefficient estimates as well as bias standard errors [see, e.g., @Blackwell2017, 318-319; @caughey2018, 254].
In light of this, recent studies measuring other latent variables have recommended incorporating their measurement uncertainty in analyses [see @solis_measuring_2020, 18; @Gandhi2020, 1553], and research examining the consequences of public opinion in the United States has done so [see, e.g., @Kastellec2015, 791-792; @caughey2018, 254].

@@

A simultaneous equation model which incorporates measurement model and structural links between variables together accounts for bias caused by simultaneity between variables and measurement models.
However, we are reluctant to use a structural equation model (SEM) because SEM is a method to test the match between the model and the data.
In other words, SEM tests whether the assumed model can be validated by the observed data, with the assumption is that the model is correct.
Therefore, SEM is subject to confirmation bias due to the existing of competing theories which we have in the theory on democracy and public opinion, omitted variables, linear causal relationship assumption, the sensitivity to the estimator choice when both endogenous and  endogenous are contaminated by measurement errors [@Edith2019], among others [@Tomarken2005].

More importantly, SEM becomes more complicated by increasing equations, demanding more from researchers on specific projects, but our main idea is to demonstrate the importance of incorporating uncertainty in a broader context but also provide a practical technique for scholars to deal with a model with multiple latent variables in both sides of the model.

The advantage of MOC is that it can accommodate multiple layers of uncertainty in both opinion estimates and substantive models [@Kastellec2015, 792] and can be used very handily.

>>>>

We proceed in three steps.
First, we reproduce the original analyses of Claassen [-@Claassen2020a; -@Claassen2020b], which included only the point estimates of the latent variable of democratic support and so exclude its measurement uncertainty.
Second, we collect the original cross-national survey data, replicate the latent variable measure of democratic support used in the two articles, and conduct the articles' analyses again, this time maintaining the entire distribution of estimates of democratic support in each country-year.^[Additional details on this data replication process are found in Supplementary Information Appendix \@ref(dgp).]
As democracy is also a latent variable in these analyses, we include the uncertainty in its estimates as well, along with that for corruption in the models of @Claassen2020b.
We also include the uncertainty for GDP and Resource Dependence variables by using multiple imputation.
In the third step, we collect even more survey data---increasing these source data by one-third---and re-estimate the two articles' analyses once more, again maintaining the full distribution of estimates to preserve measurement uncertainty.^[We also attempted to make fuller use of the available survey data by employing the DCPO model [@Solt2020a], which unlike the [@Claassen2019] model does not dichotomize ordinal responses.  The better fit of the DCPO model to the data on democratic support [see @Solt2020a, 10-12] and the additional information it incorporates, however, did not yield substantively different results; see Supplementary Information Appendix \@ref(dcpo).]

@@

Although measurement uncertainty has not yet attracted attention in the field of comparative public opinion [see, in addition to the works examined here, @OGrady2019], latent variables are estimated with a quantifiable amount of measurement errors, and measurement errors can reverse the sign of estimation of coefficients [@Bound2001, 3709; @Saccenti2020, 8], attenuate or exaggerate coefficient estimates as well as bias standard errors [see, e.g., @Blackwell2017, 318-319; @caughey2018, 254].
In light of this, recent studies measuring other latent variables have recommended incorporating their measurement uncertainty in analyses [see @solis_measuring_2020, 18; @Gandhi2020, 1553], and research examining the consequences of public opinion in the United States has done so [see, e.g., @Kastellec2015, 791-792; @caughey2018, 254].

@@

As an alternative way, a structural equation model(SEM) which incorporates measurement model and structural links between variables together can also account for bias caused by simultaneity between variables and measurement models.
However, SEM is a method to test the match between the model and the data, subject to confirmation bias due to the existing of competing theories which we have in the theory on democracy and public opinion, omitted variables, linear causal relationship assumption, the sensitivity to the estimator choice when both endogenous and endogenous are contaminated by measurement errors [@Umeh2019], among others [@Tomarken2005].

In contrast, MOC is flexible to accommodate not only various models but also multiple layers of uncertainty in both opinion estimates and substantive models [@Kastellec2015, 792] where the model and joint distribution of the error and all the variables in the model determine the bias introduced by measurement errors [@Bound2001, 3708].
